---
title: "Anti-BEPS measures Criteria"
author: "Wouter Lips"
date: "29 augustus 2017"
output: html_document
---

This will call the necessary libraries

```{r}
library(rvest)
library(stringr)
library(tabulizer)
library(xlsx)
```

This will call the list of countries and create a dataframe: Anti-BEPS, in which we will bind everything

```{r}
countries <- read.csv("data/List of EU Countries.csv", stringsAsFactors = FALSE)
colnames(countries) <- "Countries"
countries$Countries <- trimws(countries$Countries)
antiBEPS <- data.frame(countries$Countries, stringsAsFactors = FALSE)
colnames(antiBEPS) <- "jurisdictions"
```

As initatial criterion, we only have the expressed intention to implement BEPS minimal standards to go on. We'll also check for signature of the MLI.

```{r}
#signature MLI
tables <- extract_text("http://www.oecd.org/tax/treaties/beps-mli-signatories-and-parties.pdf")
for(i in 1:nrow(countries)){
  if (grepl(antiBEPS$jurisdictions[i], tables, ignore.case = TRUE) == TRUE) {antiBEPS$MLI[i] <- "yes"}
  else {antiBEPS$MLI[i] <- "no"}
}

#BEPS inclusive Framework?
tables <- extract_text("http://www.oecd.org/tax/beps/inclusive-framework-on-beps-composition.pdf")
for(i in 1:nrow(countries)){
  if (grepl(antiBEPS$jurisdictions[i], tables, ignore.case = TRUE) == TRUE) {antiBEPS$Inclf[i] <- "yes"}
  else {antiBEPS$Inclf[i] <- "no"}
}

```

Determine if jurisdiction passes criterion Anti BEPS

```{r}
for(i in 1:nrow(antiBEPS)){
  if (antiBEPS$Inclf[i] == "yes") {antiBEPS$criterion3[i] <- "yes"}
  else {antiBEPS$criterion3[i] <- "no"}
  
}

```

Cleanup and write CSV

```{r}
antiBEPS <- antiBEPS[,c(1,4,3,2)]
colnames(antiBEPS) <- c("jurisdiction", "Passes Implementation of Anti-Beps Measures", "Member of the Inclusive Framework on BEPS", "Signatory of the MLI")
write.csv(antiBEPS, file = "outcomes/Criterium Anti BEPS-EU.csv", row.names = FALSE)
#replace yes and no with x and empty
antiBEPS <- as.data.frame(sapply(antiBEPS,gsub,pattern="yes",replacement="x"))
antiBEPS <- as.data.frame(sapply(antiBEPS,gsub,pattern="no",replacement=""))

write.csv(antiBEPS, file = "outcomes/Criterium Anti BEPS-EU (with X'es).csv", row.names = FALSE)
write.xlsx(antiBEPS, file = "final blacklist/final blacklist-EU.xlsx", sheetName = "Anti-BEPS measures", row.names = FALSE, col.names = TRUE, append = TRUE, showNA = FALSE)
```



